Tidy data structure to support exploration and modeling of temporal data

### 2018-11-26 main.Rmd
added one more paragraph to sub-section on "index"

A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than an attribute, which makes time accessible to users. For example, one could easily extract time components, such as time of day and day of week, from the index to visualise seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. But if the "index" is employed as attributes, analysts would write these simple queries in a programmatic manner, which can be avoidable from an analytic point of view.

>>>>

A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than an attribute, which makes time accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. But if the "index" is employed as attributes, analysts would write these simple queries in a programmatic manner, which can be avoidable from an analytic point of view.

A number of time classes are supported and easily extensible to new types. The base line is that time indices can be potentially ordered in past to future. Characters cannot be ordered, so a variable hosting characters will make it unsupported for index. Ordered factors, however, can be immediately recognized as valid index. For instance, month names have a natural ordering from January to December, and so are weekdays from Monday to Sunday.
